{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Variational analysis, and Applications }

### 2024-12-23 Notebook LaTEX/Proposal/main.tex
>w<, changes

    \begin{align}

@@

    \end{align}\label{eqn:nag_example}

@@

    Chambolle, Dossal showed that by choosing sequence $(t_k)_{k \ge 1}$ to be $t_k = $

>>>>

    \begin{align}\label{eqn:nag_example}

@@

    \end{align}

@@

    \todo{Cite them. }{\hl{Chambolle, Dossal}} showed that by choosing sequence $(t_k)_{k \ge 1}$ to be $t_k = (n + a - 1)/a$ where $a > 2$ instead would give $(x_k)_{k \ge 0}$ weak convergence in Hilbert space. 
    It's put as an open question on what happens to the iterates when $a = 2$. 
    All of these seemingly raises a crucial question: ``Is it possible to describe something about the NAG algorithm for a set of sequence that is non-traditional?''.
    Or rephrase it more clearly: ``What is the weakest description of momentum sequence $(\theta_k)$ such that we can still claim something of value about the NAG algorithm?''
